---
title: "NHS Adult Cardiac Surgery Performance"
output: html_notebook
---

Data sourced from [NHS Datasets](https://www.nhs.uk/about-us/nhs-website-datasets/) at [Cardiac Surgery Perfomance Indicators](http://media.nhschoices.nhs.uk/data/foi/TransparencyIndicatorsCardiacSurgeryPerformance.csv) **8th September 2018**

#### Fetching and cleaning the raw data
```{r}
raw = read.csv("TransparencyIndicatorsCardiacSurgeryPerformance.csv")
raw = select(raw, -Text)
raw$Value = as.numeric(gsub("%", "", raw$Value))

operations = filter(raw, `MetricName` == "Number of operations")
operations = rename(operations, `Operations` = "Value")
operations = select(operations, -MetricName)

successRate = filter(raw, `MetricName` != "Number of operations")
successRate = rename(successRate, `Success Rate` = "Value")
successRate = select(successRate, OrganisationID, `Success Rate`)

surgery = merge(operations, successRate, by = "OrganisationID")
surgery$`Failed Operations` = trunc((surgery$Operations / 100) * surgery$`Success Rate`)
surgery$`Successful Operations` = trunc(surgery$Operations - ((surgery$Operations / 100) * surgery$`Success Rate`))

```

We now have the raw data lets see a quick summary
```{r}
summary(select(surgery, -OrganisationID, -OrganisationCode, -OrganisationName))
```

...now plot the success rate 

```{r}
plot(surgery$Operations, surgery$`Success Rate`,
       main="Adult Cardiac Surgery No. Operations vs Success Rate",
       xlab="No. Operations",
       ylab="Success Rate",
       col= "blue", pch = 1, cex = 1, lty = "solid", lwd = 2)

text(surgery$Operations, surgery$`Success Rate`, labels=surgery$OrganisationCode, cex= 0.5, pos=2)
```

The data arranged by 'Success Rate` in descending order
```{r}
arrange(select(surgery, OrganisationID, OrganisationCode, OrganisationName, Operations, `Successful Operations`, `Failed Operations`, `Success Rate`), desc(`Success Rate`))

```

#### Observations

**RJ701** St George's Hospital London, jumps out at you immediately when viewing the chart, it seems to be performing particularly bad.

**RGM21** Royal Papworth Hospital. Given the number of operations performed it achieves a consistently high level of successfully performed procedures. 
